NanoMaLy

### 2015-11-19 paper/pldi16-submission/interactive.tex
down to 11pp

\paragraph{Collecting Edges}
%
Next, we describe the general recipe for extending a transition
rule to collect edges, and provide a selection of examples
in Figure~\ref{fig:interactive}.
%
The steps-to edges are collected by recording the consequent of
each original rule in the trace. That is, each original judgment
\step{e}{\vsu}{e'}{\vsu'} becomes
\stepg{e}{\vsu}{\tr}{e'}{\vsu'}{\singlestep{e}{e'}; \tr}.
%
The sub-term edges are delegated to a helper function \subtermssym\
which adds edges from an expression to each of its
\emph{immediate} sub-expressions.
%
We collect \subtermssym edges after each transition,
to get the following template for the small-step relation:
\[
\stepg{e}{\vsu}{\tr}{e'}{\vsu'}{\singlestep{e}{e'}; \subterms{e'}; \tr}
\]
\RJ{shouldn't this be $\subterms{e}$?}

@@

Given a reduction graph $G$ and an initial path
$p = \singlestep{e_1}{\singlestep{e_2}{e_n}}$, such that
\stepsg{e_1}{\emptysu}{\bullet}{e_n}{\su}{\tr}, we define the following
traversals in Figure~\ref{fig:traversing-graph}:
%
\begin{itemize}
\item \stepforwardsym takes a single step forward.
\item \stepbackwardsym takes a single step backward.
\item \jumpforwardsym takes a ``big'' step forward to the next function call.
\item \jumpbackwardsym takes a ``big'' step backward to the previous function call.
\item \stepintosym steps into a function call in a sub-term, isolating it from the context.
\item \stepoversym steps over a function call in a sub-term.
\end{itemize}
%
The initial path $p$ is required for the backward-steps as a node may
have multiple incoming $\leadsto$ edges, \eg
\singlestep{\eplus{1}{2}}{3} and \singlestep{\eplus{2}{1}}{3}.
%
The sub-term edges $\searrow$ allow us to decompose an expression into a
sub-expression and the surrounding context, thus enabling the \stepintosym
and \stepoversym traversals.
%

@@

% \begin{itemize}
% \item extend operational semantics to collect reduction graph
% \item nodes are terms, edges indicate ``steps-to'' and ``sub-term'' relations
% \item visualize path through reduction graph
% \item expand edges to reveal more fine-grained steps (step/jump forward/backward)
% \item never lose context (unlike traditional debugger)
% \end{itemize}

>>>>

\paragraph{Collecting Edges}
%
Next, we describe the general recipe for extending a transition
rule to collect edges, and provide a selection of examples
in Figure~\ref{fig:interactive}.
%
The steps-to edges are collected by recording the consequent of
each original rule in the trace. That is, each original judgment
\step{e}{\vsu}{e'}{\vsu'} becomes
\stepg{e}{\vsu}{\tr}{e'}{\vsu'}{\singlestep{e}{e'}; \tr}.
%
The sub-term edges are delegated to a helper function \subtermssym\
which adds edges from an expression to each of its
\emph{immediate} sub-expressions.
%
We collect \subtermssym edges after each transition,
to get the following template for the small-step relation:
\[
\stepg{e}{\vsu}{\tr}{e'}{\vsu'}{\singlestep{e}{e'}; \subterms{e'}; \tr}
\]

@@

Next, we show how to build an visual interactive debugger
from the traced semantics, by describing the visualization
\emph{state} \ie\ what the user sees at any given moment,
the set of \emph{commands} available to user, and what
they do, and finally how we use a command to \emph{update}
the visualization state. In the sequel, for clarity of
exposition, we assume we have a (global) trace:
$\stepg{e}{\emptysu}{\bullet}{e'}{\vsu'}{\tr}$.

\paragraph{State}
A \emph{visualization state} is ...
The \emph{initial state} is the graph containing the single edge
${e \hookrightarrow \stuck}$.
+ Visualization = ExprGraph + invariants (unique predecessor) -- link to figure.

\paragraph{Commands}
\begin{itemize}
\item \stepforwardsym\ takes a single step forward.
\item \stepbackwardsym\ takes a single step backward.
\item \jumpforwardsym\ takes a ``big'' step forward to the next function call.
\item \jumpbackwardsym\ takes a ``big'' step backward to the previous function call.
\item \stepintosym\ steps into a function call in a sub-term, isolating it from the context.
\item \stepoversym\ steps over a function call in a sub-term.
\end{itemize}

\paragraph{Update}
Figure~\ref{fig:traversing-graph} shows how we update the state for each
command...
%
find   :: Vis -> Cmd -> Expr
update :: Vis -> Cmd -> Vis
%
The initial path $p$ is required for the backward-steps as a node may
have multiple incoming $\leadsto$ edges, \eg
\singlestep{\eplus{1}{2}}{3} and \singlestep{\eplus{2}{1}}{3}.
%
Note that the sub-term edges $\searrow$ allow us to decompose an expression into a
sub-expression and the surrounding context, thus enabling the \stepintosym
and \stepoversym traversals.

data Sel = Expr

data Vis = { graph :: TraceGraph, edges = ExprGraph  }

path :: Vis -> Expr -> [Expr]
stepX :: Sel -> Vis -> Vis(edited)

path v e = graphPath (graph v,  root (v, e),  e)

putBefore, putAfter :: EGraph -> Expr -> Expr -> EGraph
putRoot  :: EGraph -> Expr -> EGraph
getRoot  :: EGraph -> Expr -> Expr

pathToRoot  ::

@@
